HTW E1 Testing

### 2024-03-12 Analysis/e1_test.qmd
cleanup; re-render; add some more reject model fits
full exp 1 results; more hybrid fits; combo brms models; e1 bandType brms models

---
title: "HTW E1 Testing"
categories: [Analysis, R, Bayesian]
---

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

>>>>

---
title: "HTW E1 Testing"
categories: [Analyses, R, Bayesian]
---

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
